Fisheries example integrating FLR

### 2018-05-04 notebook/ms/SI5.Rmd

---
title: "Fisheries example integrating FLR"
author: A. Bradley Duthie&#xb9;&#xb3;, Jeremy J. Cusack&#xb9;, Isabel L. Jones&#xb9;,
  Jeroen Minderman&#xb9;, Erlend B. Nilsen&#xb2;, Roc&#0237;o A. Pozo&#xb9;, O. Sarobidy
  Rakotonarivo&#xb9;, Bram Van Moorter&#xb2;, and Nils Bunnefeld&#xb9;
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2] Norwegian Institute for Nature Research, Trondheim, Norway [3] alexander.duthie@stir.ac.uk'
output:
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
header-includes: null
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: gmse.bib
subtitle: 'GMSE: an R package for generalised management strategy evaluation (Supporting
  Information 5)'
biblio-style: apalike
---

>>>>

---
title: "Fisheries example integrating FLR"
author: A. Bradley Duthie&#xb9;&#xb3;, Jeremy J. Cusack&#xb9;, Isabel L. Jones&#xb9;,
  Jeroen Minderman&#xb9;, Erlend B. Nilsen&#xb2;, Roc&#0237;o A. Pozo&#xb9;, O. Sarobidy
  Rakotonarivo&#xb9;, Bram Van Moorter&#xb2;, and Nils Bunnefeld&#xb9;
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2] Norwegian Institute for Nature Research, Trondheim, Norway [3] alexander.duthie@stir.ac.uk'
output:
  html_document: default
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes: null
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: gmse.bib
subtitle: 'GMSE: an R package for generalised management strategy evaluation (Supporting
  Information 5)'
biblio-style: apalike
---
